\cursedforest\ - A Random Forest Implementation for ``Big'' and ``Wide'' Data \\ Supplementary Information

### 2016-12-18 doc/publications/plos16/plos16.tex

\begin{table}[!ht]
\begin{minipage}{\textwidth}
%\begin{adjustwidth}{-2.25in}{0in} % Comment out/remove adjustwidth environment if table fits in text column.
\centering
\caption{ {\bf Performance comparison between the different machine learning algorithms.}}
\begin{tabular}{|l|l|l|l|l|l||}
\hline
\bf{Genome \%}                      & \bf{Method} & \bf{Error}  & \bf{Runtime}  \\
\hline

\multirow{3}{*}{phase1\_chr22: 1,092 x 490,036} & \cursedforest\ & 0.04  & 1 min 50 seconds                        \\
                                                & RF - Spark ML  &  0.05           &           7 min 44 seconds         \\
                                                & randomForest - R         & 0.05       & 24 min           \\
                                                & ranger - R      & 0.06       & 1 min 10 seconds       \\
                                                & ranger - c++     & 0.06       & 7 min            \\

 \hline
\multirow{3}{*}{phase3\_chr22: 2,504 x 1,103,548}   &               &            &                  \\
                                                    & randomForest - R      & NA         & NA                \\
                                                    & H2O           & 0.05       & 16 hours         \\
                                                    & ranger - R    & 0.06       & 4 min 30 seconds     \\
\hline
\multirow{3}{*}{phase3\_chr1: 2,504 x 6,450,364}    & \cursedforest\ & 0.063  & 1hr 58min         \\
                                                    & RF - Spark ML  & 0.04       & 8hr 29min        \\
                                                    & ranger - R      &  0.05       & 28 mins         \\
\hline
\multirow{3}{*}{phase3\_chr1-3: 2,504 x 19,328,051} & \cursedforest\ & 0.046  & 4hr 0min               \\
                                                    & RF - Spark ML  &    NA         &   NA               \\
                                                    & ranger - R      & 0.03      &         \\
                                                    & ranger - R        &             0.973     &      03:58           \\
\hline

\multirow{4}{*}{phase3\_chr1-22: 2,504 x 81,047,467} & \cursedforest\ & XX  & 7hr 14min \\
& Spark ML & NA & NA  \\
& ranger (C++)       &        NA     &        NA      \\
\hline
\end{tabular}
\begin{flushleft} 
Comparison of different various machine learning libraries on different subsets of variant data 
from the 1000 Genomes Project.
Each random forest model consists of 50 trees.
\end{flushleft}
\label{timingtable}
%\end{adjustwidth}
\end{minipage}
\end{table}

>>>>

\begin{table}[!ht]
\begin{minipage}{\textwidth}
%\begin{adjustwidth}{-2.25in}{0in} % Comment out/remove adjustwidth environment if table fits in text column.
\centering
\caption{ {\bf Performance comparison between the different random forest implementations.}}
\begin{tabular}{|l|l|l|l|l|l||}
\hline
\bf{Genome \%}                      & \bf{Method} & \bf{Error}  & \bf{Runtime}  \\

\hline

\multirow{5}{*}{phase1\_chr22: 1,092 x 490,036} & \cursedforest\ & 0.04  & 1 min 50 seconds                        \\
                                                & Spark ML  &  0.05           &           7 min 44 seconds         \\
                                                & randomForest (R)         & 0.05       & 24 min           \\
                                                & ranger (R)      & 0.06       & 1 min 10 seconds       \\
                                                & ranger (C++)     & 0.06       & 7 min            \\

\hline

\multirow{5}{*}{phase3\_chr22: 2,504 x 1,103,548}   & \cursedforest\ & 0.06 & 4 min 2 seconds \\
                                                    & Spark ML  & 0.06 & 37 min 19 seconds \\
                                                    & randomForest (R)        & NA         & NA                \\
                                                    & ranger (R)    & 0.06       & 4 min 30 seconds     \\
                                                    & H2O           & 0.05       & 16 hours         \\

\hline

\multirow{3}{*}{phase3\_chr1: 2,504 x 6,450,364}    & \cursedforest\ & 0.04  & 19 min 19 seconds         \\
                                                    & Spark ML  & 0.04       & 8 hour 29 min        \\
                                                    & ranger (R)      &  0.05       & 28 mins         \\
\hline

\multirow{3}{*}{phase3\_chr1-3: 2,504 x 19,328,051} & \cursedforest\ & 0.02  & 56 min 43 seconds             \\
                                                    & Spark ML &    NA         &   NA               \\
                                                    & ranger (R)      & 0.03      &    3 hour 58 min     \\
\hline

\multirow{4}{*}{phase3\_chr1-22: 2,504 x 81,047,467} & \cursedforest\ & XX  & 7hour 14min \\
                                                    & Spark ML & NA & NA  \\
                                                    & ranger (R)       &        NA     &        NA    \\
                                                    & ranger (C++)       &        NA     &        NA    \\
\hline

\end{tabular}
\begin{flushleft} 
Comparison of different various machine learning libraries on different subsets of variant data 
from the 1000 Genomes Project.
Each random forest model consists of 50 trees.
\end{flushleft}
\label{timingtable}
%\end{adjustwidth}
\end{minipage}
\end{table}
